Almost compatible functions and infinite length games

### 2017-01-24 articles/almost-compatible-functions-and-topological-games/article.tex
final revisions per referee

  In \cite{MR1129143}, Scheepers noted that \(\alcompS{\omega_1}\) holds in \(ZFC\),
  and that it is possible to force \(\mf c\) to be arbitrarily large
  while preserving \(\alcompS{\mf c}\). However, \(\alcompS{\mf c^+}\) always fails.
  This axiom may be applied to obtain a winning \(2\)-tactic for \(\pl F\)
  in the countable-finite game.

@@

  We now construct a topology on \(\omega_n\) for each \(n<\omega\) which
  will witness a Kurepa family of size \(\aleph_n\), exploiting a theorem of
  Juh\'asz et. al. in \cite{MR539228}.

@@

  As noted in \cite{MR1229125}, Jensen's one-gap two-cardinal theorem under
  \(V=L\) introduced in \cite{MR0309729} implies that \(\kurepaS\kappa\)
  holds for all cardinals \(\kappa\).

  \begin{corollary}[\(V=L\)]\label{alcompSPunderV=L}
    \(\alcompSP{\kappa}\) for all cardinals \(\kappa\).
  \end{corollary}

@@

  We are also able to force \(\alcompSP{\kappa}\) to fail for every cardinal
  other than the first \(\omega\)-many we've already guaranteed.

@@

  \begin{figure}[ht]
\begin{center}
\begin{tikzpicture}[x=0.8in,y=0.5in]
  \node at (-3.5,2) {\(\alcompS\kappa\)};
  \node at (-3.5,0) {\(\pl F \ktactwin2\schFillStrictGame\kappa\)};
  \node at (0,2) {\(\alcompSP\kappa\)};
  \node at (-1,1) {\(\pl F \kmarkwin2\menGame{\oneptlind\kappa}\)};
  \node at (0,1) {\(\Leftrightarrow\)};
  \node at (1,1) {\(\pl F \kmarkwin2\schFillIntGame\kappa\)};
  \node at (-1,0) {\(\pl F \kmarkwin2\schFillInitialGame\kappa\)};
  \node at (0,0) {\(\Leftrightarrow\)};
  \node at (1,0) {\(\pl F \kmarkwin2\schFillGame\kappa\)};
  \node at (0,-1) {\(\pl F \kmarkwin2\schFillStrictGame\kappa\)};
  \draw[-implies,double equal sign distance] (-3.2,2) -- (-0.3,2);
  \draw[-implies,double equal sign distance] (-2.6,0) -- (-1.9,0);
  \draw[-implies,double equal sign distance] (-3.5,1.65) -- (-3.5,0.35);
  \draw[-implies,double equal sign distance] (0,1.65) -- (0,1.35);
  \draw[-implies,double equal sign distance] (0,0.65) -- (0,0.35);
  \draw[-implies,double equal sign distance] (0,-0.35) -- (0,-0.65);
\end{tikzpicture}
\end{center}
\caption{Diagram of Scheeper/Menger game implications with \(\alcompS{\kappa},\alcompS{\kappa}\)}
\label{GamesDiagram}
\end{figure}

>>>>

  In \cite{MR1129143}, Scheepers noted that \(\alcompS{\omega_1}\) holds in \(ZFC\),
  and that it is possible to force \(\mf c\) to be arbitrarily large
  while preserving \(\alcompS{\mf c}\); however,
  it was also shown that \(\alcompS{\mf c^+}\) always fails.
  This axiom may be applied to obtain a winning \(2\)-tactic for \(\pl F\)
  in the countable-finite game.

@@

  We now make use of
  a topology on \(\omega_n\) for each \(n<\omega\) that
  witnesses a Kurepa family of size \(\aleph_n\), due to a theorem of
  Juh\'asz et. al. in \cite{MR539228}.

@@

  As noted in \cite{MR1229125}, Jensen's one-gap two-cardinal theorem under
  \(V=L\) introduced in \cite{MR0309729} implies that \(\kurepaS\kappa\),
  and therefore \(\alcompSP\kappa\), holds for all cardinals \(\kappa\).
  However, the authors wish to thank their anonymous referree for
  observing the following improvement:

  \begin{corollary}\label{alcompSPunderV=L}
    Assume the covering lemma over the Core Model holds. Then
    \(\alcompSP{\kappa}\) holds for all cardinals \(\kappa\).
  \end{corollary}

  \begin{proof}
    Juh\'asz and Weiss note in \cite[pg. 186]{juhaszgood} that the covering
    lemma over the Core Model guarantees \(\splendidS\kappa\), and therefore
    \(\kurepaS\kappa\) and \(\alcompSP\kappa\), when
    \(\cf\kappa>\omega\).
  \end{proof}

@@

  We are also able to force \(\alcompSP{\kappa}\) to fail for every cardinal
  other than the first \(\omega\)-many we've already guaranteed. The authors
  again thank the referee for observing that the following result
  contrasts very nicely with Corollary \ref{alcompSPunderV=L}: large cardinals
  are necessary to find \(\kappa>\aleph_\omega\) with \(\cf\kappa>\omega\)
  where \(\splendidS\kappa\) fails.

@@

  \begin{figure}[ht]
\begin{center}
\begin{tikzpicture}[x=0.8in,y=0.5in]
  \node at (-3.5,2) {\(\alcompS\kappa\)};
  \node at (-3.5,0) {\(\pl F \ktactwin2\schFillStrictGame\kappa\)};
  \node at (0,2) {\(\alcompSP\kappa\)};
  \node at (-1,1) {\(\pl F \kmarkwin2\menGame{\oneptlind\kappa}\)};
  \node at (0,1) {\(\Leftrightarrow\)};
  \node at (1,1) {\(\pl F \kmarkwin2\schFillIntGame\kappa\)};
  \node at (-1,0) {\(\pl F \kmarkwin2\schFillInitialGame\kappa\)};
  \node at (0,0) {\(\Leftrightarrow\)};
  \node at (1,0) {\(\pl F \kmarkwin2\schFillGame\kappa\)};
  \node at (0,-1) {\(\pl F \kmarkwin2\schFillStrictGame\kappa\)};
  \draw[-implies,double equal sign distance] (-3.2,2) -- (-0.3,2);
  \draw[-implies,double equal sign distance] (-2.6,0) -- (-1.9,0);
  \draw[-implies,double equal sign distance] (-3.5,1.65) -- (-3.5,0.35);
  \draw[-implies,double equal sign distance] (0,1.65) -- (0,1.35);
  \draw[-implies,double equal sign distance] (0,0.65) -- (0,0.35);
  \draw[-implies,double equal sign distance] (0,-0.35) -- (0,-0.65);
\end{tikzpicture}
\end{center}
\caption{Diagram of Scheeper/Menger game implications with \(\alcompS{\kappa},\alcompSP{\kappa}\)}
\label{GamesDiagram}
\end{figure}
